experDesign: stratifying samples into batches with minimal bias

### 2024-05-20 README.Rmd
Export position_name

The goal of experDesign is to help you manage your samples before an experiment but after they are collected.
For example, checking for common problems in the data, and help reduce or even prevent batch bias before performing an experiment, or measure once it is already done
It provides four main functions:

@@

@@

If you are still designing the experiment and do not have collected any data [DeclareDesign](https://cran.r-project.org/package=DeclareDesign) might be relevant for you.

>>>>

The goal of experDesign is to help you distribute your samples before an experiment but after they are collected. 
For example, checking for common problems in the data, and reducing or even preventing batch bias before performing an experiment, or measuring it once the experiment is performed.
It provides four main functions:

@@

There are other helpers.

@@

If you are still designing the experiment and do not have collected any data [DeclareDesign](https://cran.r-project.org/package=DeclareDesign) might be relevant for you. But specially the [randomizr](https://cran.r-project.org/package=randomizr) packages  which makes common forms of random assignment and sampling.
